\textbf{Suggestions for improving invited speaker diversity to reflect trainee diversity}

### 2020-02-07 submission/Table_1.Rmd
finish revisions and format resubmission

---
geometry: margin=1.0in
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
---
\begin{center}
\captionof{table}{Suggestions and resources to increase invited speaker diversity.}
\small
\centering
\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{}m{5cm}}

@@

Create a list & Use the GitHub template to create a self-nomination list and resource for your field & https://github.com /diversifymicrobiology /DiversifyMicrobiology.github.io \\\hline

@@

Encourage trainees to engage & \makecell[l]{When a talk is over, ensure that \\trainees are the first to ask questions} & \\\hline

>>>>

---
geometry: margin=1.0in
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  word_document: default
---
\begin{center}
\captionof{table}{Suggestions and resources to increase invited speaker diversity.}
\small
\centering
\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{\centering\arraybackslash}m{5cm}}

@@

Create a list & Use the GitHub template to create a self-nomination list and resource for your field & Template can be found at https://github.com /diversifymicrobiology /DiversifyMicrobiology.github.io \\\hline

@@

Encourage trainees to engage & When a talk is over, ensure that trainees are the first to ask questions & \\\hline
